DOpElib:\\ Differential Equations and Optimization Environment

### 2018-08-07 Examples/Documentation/introduction.tex
Changes in the introduction: cleaning typos, cleaning test in foreword and intro, new Section 2.3, new Chapter 8

@@

\begin{remark}
Our current DOpE installation has been successfully tested for deal.II version 8.5.0.
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Installation}\label{sec_installation}
To work with DOpElib, your need necessarily deal.II, which installation 
we describe first. Afterwards, the DOpElib installation is described and finally
other optional packages might be installed.
\begin{itemize}
\item We automatically search for \texttt{deal.II} to your home
  directory, i.e., if \texttt{deal.II} is located in \\
\texttt{\textasciitilde/deal.II} you don't have to do anything. 
\item Alternatively, if you prefer another position you can install it anywhere but need 
to set the \texttt{DEAL\_II\_DIR} environment variable, so that it 
will be found by cmake, i.e.,
\begin{lstlisting}
export DEAL_II_DIR=[path to deal.ii]
\end{lstlisting}
\begin{remark}
\textbf{Be careful} if you work in several terminal windows and have several deal.II versions. In this case, the
export-command might have to be done again in that new window. Otherwise
another deal.II version might be linked resulting in linker errors or
segmentation faults without useful error message. In order to check to which
deal.II version DOpE is linked, type 
\begin{lstlisting}
echo ${DEAL_II_DIR}
\end{lstlisting}
in the current terminal window.
\end{remark}
\begin{remark}
\textbf{Furthermore:} please make sure that you point in the above path 
to the deal.II \texttt{install} folder and NOT in the main directory of your deal.II 
installation.
\end{remark}

Detailed installing instructions for deal.II (here the last version
8.4.0) can be found on 
\texttt{http://www.dealii.org/8.4.0/readme.html}. The deal.II 
installation instructions are descriptive enough and we omit 
any further comments and refer to their webpage.
%

>>>>

\section{Contact / Mailinglist}
We encourage you to contact us in case you have questions:
\begin{verbatim}
dope@dopelib.net 
\end{verbatim}

@@

\begin{remark}
Our current \dope{} installation has been successfully tested for deal.II version 9.0.0.
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Installation}\label{sec_installation}
Having deal.II and other possible libraries installed, we turn now our focus 
to the installation of \dope{} itself:
\begin{itemize}
\item We automatically search for \texttt{deal.II} to your home
  directory, i.e., if \texttt{deal.II} is located in \\
\texttt{\textasciitilde/deal.II} you don't have to do anything. 
\item Alternatively, if you prefer another position you can install it anywhere but need 
to set the \texttt{DEAL\_II\_DIR} environment variable, so that it 
will be found by cmake, i.e.,
\begin{lstlisting}
export DEAL_II_DIR=[path to deal.ii]
\end{lstlisting}
\begin{remark}
\textbf{Be careful} if you work in several terminal windows and have several deal.II versions. In this case, the
export-command might have to be done again in that new window. Otherwise
another deal.II version might be linked resulting in linker errors or
segmentation faults without useful error message. In order to check to which
deal.II version DOpE is linked, type 
\begin{lstlisting}
echo ${DEAL_II_DIR}
\end{lstlisting}
in the current terminal window.
\end{remark}
\begin{remark}
\textbf{Furthermore:} please make sure that you point in the above path 
to the deal.II \texttt{install} folder and NOT in the main directory of your deal.II 
installation.
\end{remark}

Detailed installing instructions for deal.II (here the last version
9.0.0) can be found on 
\url{http://www.dealii.org/9.0.0/readme.html}. These
installation instructions are descriptive enough and we omit 
any further comments and refer to their webpage.
%
